Operational adoption of new probabilistic point rainfall forecasts: the crucial role of a user-centric training

### 2021-03-17 manuscript/main.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%
% Background
\section{Background}
\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/Background_AnnualRainfall_Location_H_CR.png}}
\caption{Firstly, the flowchart describes the experiment processes that follow in the two experiment phases (real-time and offline). Secondly, the flowchart describes who, between developers (red squares), testers (blue squares) and developers & testers (cyan squares), conducted the experiment processes. Finally, the flowchart describes the possible experiment outcomes.}
\label{Location_Annual_Rainfall_H_CR}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%
% Background
\section{Background}
\begin{figure*}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/Background_Location_Orography_AnnualRainfall_H_CR.png}}
\caption{Panel (a) shows the climatological regions in which Costa Rica is divided, whilst panel (b) shows the administrative regions (colours shades) and counties (white lines) in which Hungary is divided. Panel (c) and (d) show the orography in Costa Rica and Hungary, respectively. Panel (d) and (e) show the annual rainfall (in mm) in Costa Rica and Hungary, respectively.}
\label{Location_Annual_Rainfall_H_CR}
\end{figure*}
